Keystoneness, centrality, and the structural controllability of ecological networks

### 2019-01-14 paper/reviewers-response.Rmd

> "In the literature on ecological networks, the term keystone species has often been tossed around without any clear definition. I was pleased to read that here the authors have developed a cleaner, more effective way to identify keystone species in ecological networks than methods that have been proposed before. I think the authors have made the correct choice in emphasizing the conceptual aspects of the approach, and do so quite well. The background on control theory was complex but manageable to read and understand in this context."

We are very thankful for the positive feedback.

> "Overall I found the paper well-written and sound, but there were a few questions I had that could improve clarity in the methods used. In the glm that used nD as the response variable, is there any concern that including N (number of species) as a predictor may cause a problem when the response is D/N? I can understand why this was included, but I can also imagine this resulting in models that show an effect of N when there is none (I could be wrong on this)."

Thanks for the observation. As you mention, we believe it is ok to include the sample size as a predictor in this model for three reasons. First, there are several instances when the probability of something occurring increases or decreases with sampling effort, etc. It *does* imply a non-linear relationship though. Second, if there were a relationship between N on D, then using D/N (as opposed to of D) as the response variable and N as a predictor would actually reduce the size of the effect of N, rather than amplify it. If on the other hand, N and D are completely decoupled, then using D/N as the response variable should affect the intercept but not the coefficient of D. Third, in any case we only found a comparatively small effect of N on D. Although it might be relevant statistically it seems to be ecologically insignificant. 
<!-- FDO: Daniel, could you please double check this makes sense? -->

### 2019-01-14 paper/manuscript.Rmd
Respond to question about using N as a predictor of D/N
Improve explanation about random effects in controllability models

After finding the minimum driver-node set in each of our networks, we wanted to test whether invasion status or other predictors are correlated to controllability. 
We do this using a set of generalised linear models with binomial error structure. 
The response variable was the relative size of the minimum driver-node set $n_D$ of the twenty empirical networks (ten invaded and ten uninvaded), and we included invasion status as a predictor. 
As predictors, we also include the network connectance, the network nestedness (NODF), the number of species [since one might naively expect to see a negative relationship between richness and controllability; @menge_indirect_1995], the network asymmetry (an indication of the balance between plant and pollinator diversity), and the interaction strength asymmetry [the asymmetry on the dependences between trophic levels; @bluthgen_specialization_2007]\R{R2-citation-with-name}.
We compared models using the Akaike Information Criterion for small sample sizes (AICc).

@@

\R{R2-one-lumped-model-a}We then examined how species-level properties were related to control capacity using a set of candidate generalised linear models with binomial error structure. 
These models included five predictor variables that mirror the network-level predictors. 
First, the species' contribution to nestedness, which has been proposed as a key feature that promotes stability and robustness in mutualistic networks [@saavedra_strong_2011]. 
Second,\R{R2-species-strength-a} the species' strength (the sum of a species' visits), which quantifies the strength of a species' associations and is indirectly related to its abundance [@poisot_comparative_2012]. 
Third, the direction of asymmetry which quantifies the net balance in dependencies; that is, it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007]. 
Fourth, the species' degree in order to account for the intrinsic centrality of a species.
Finally, we included a categorical variable for the species' trophic level (plant or pollinator) and an interaction term between trophic level and the previous four variables. 
To facilitate comparison between predictors, degree and visitation strength were log-transformed and all four continuous variables were scaled to have a mean of zero and a standard deviation of one. 
\R{R2-one-lumped-model-b}In these models, species from all networks were analysed together. 
\R{R2-random-effects}We initially included random effects to account for possible variation across communities, but we found that the variance explained by these random effects was zero, and therefore random effects were not included in further analyses. 
\R{R2-all-candidates}We then generated all possible candidate models.
To identify the models that were best supported by the data, we first determined the most parsimonious random structure using the AICc. 
The relative importance of variables was then assessed by looking at their effect sizes in the top-ranked models and the cumulative weight of the models in which they are present.

>>>>

After finding the minimum driver-node set in each of our networks, we wanted to test whether invasion status or other predictors are correlated to controllability. 
We do this using a set of generalised linear models with Gaussian errors and a logit link function. 
The response variable was the relative size of the minimum driver-node set $n_D$ of the twenty empirical networks (ten invaded and ten uninvaded), and we included invasion status as a predictor. 
As predictors, we also include the network connectance, the network nestedness (NODF), the number of species [since one might naively expect to see a negative relationship between richness and controllability; @menge_indirect_1995], the network asymmetry (an indication of the balance between plant and pollinator diversity), and the interaction strength asymmetry [the asymmetry on the dependences between trophic levels; @bluthgen_specialization_2007]\R{R2-citation-with-name}.
We compared models using the Akaike Information Criterion for small sample sizes (AICc).

@@

\R{R2-one-lumped-model-a}We then examined how species-level properties were related to control capacity using a set of candidate generalised linear models with binomial error structure. 
These models included five predictor variables that mirror the network-level predictors. 
First, the species' contribution to nestedness, which has been proposed as a key feature that promotes stability and robustness in mutualistic networks [@saavedra_strong_2011]. 
Second,\R{R2-species-strength-a} the species' strength (the sum of a species' visits), which quantifies the strength of a species' associations and is indirectly related to its abundance [@poisot_comparative_2012]. 
Third, the direction of asymmetry which quantifies the net balance in dependencies; that is, it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007]. 
Fourth, the species' degree in order to account for the intrinsic centrality of a species.
Finally, we included a categorical variable for the species' trophic level (plant or pollinator) and an interaction term between trophic level and the previous four variables. 
To facilitate comparison between predictors, degree and visitation strength were log-transformed and all four continuous variables were scaled to have a mean of zero and a standard deviation of one. 
\R{R2-one-lumped-model-b}In these models, species from all networks were analysed together. 
\R{R2-random-effects}We initially included random effects to account for possible variation across communities, but we found that the among-group variance was effectively zero, and therefore random effects were not included in further analyses. 
\R{R2-all-candidates}We then generated all possible candidate models.
To identify the models that were best supported by the data, we first determined the most parsimonious random structure using the AICc. 
The relative importance of variables was then assessed by looking at their effect sizes in the top-ranked models and the cumulative weight of the models in which they are present.
